---
title: "Getting And Cleaning Data Course Project Code Book"
author: "Reza Zahedi"
date: "October 25, 2018"
output: github_document
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE, cache=TRUE}
source("./run_analysis.R")
allnames <- cbind(oldnames, newnames)
```

## Data Transformations and other steps in _"run_analysis.R"_ :
#### Point 1
Reading all data sets into R.

#### point 2
Merging the all the imported data sets.

#### point 3
Assigning descriptive activity names to name the activities in the data set.

#### point 4
Extracting only the measurements on the mean and standard deviation for each measurement.

#### point 5
Appropriately labeling of the data set with descriptive variable names using _regular expressions_.

#### point 6.1
First way to creat a second, independent tidy data set with the average of each variable for each activity and each subject.

#### point 6.2
Second way to creat a second, independent tidy data set with the average of each variable for each activity and each subject.


## Initial and Final variable names in data set:
```{r, echo=FALSE, message=FALSE}
library(knitr)
library(kableExtra)
library(dplyr)
allnames <- as.data.frame(allnames)

allnames <- rename(allnames, "Old Names" = "oldnames",
             "New Names" = "newnames")

kable(allnames) %>%
     kable_styling(bootstrap_options = c("striped", "hover"),
                   full_width = F)
```
